Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
fine-tune writing and finalize paper

---
title: "Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021"
title-block-banner: true
abstract: "Police strip search has always been a topic of great contention, where the question commonly raised was how certain demographics are more likely to undergo strip searches than others. Data then was gathered from Open Data Toronto to assess the correlation between strip searches and the racial and gender identities of arrested 'suspects' in the Toronto Municipal from 2020 to 2021. In short, this paper finds that police strip searches are quite racialized and gendered, especially towards people of African descent and females within Toronto. This analysis would enable us to rethink the modern form of policing, how it transpires in times of crisis and critically affects people of marginalized identities." 
thanks: "Code and data are available at: https://github.com/ponolite/Police_Arrests_and_Strip_Searches/tree/main"
author: "Quang Mai"
date: today
date-format: long
format: pdf
editor: visual
toc: true
number-sections: true
bibliography: references.bib
output: 
  pdf_document:
    extra_dependencies: ["float"]
---

@@

Regarding @fig-reasons-gender, intriguingly, the graph calls into question of the above data confirming how males are slightly more likely to be strip searched compared to females when they're arrested. However, when intersected with data like the total number of reasons attributed to strip searches, there appears to be a trend of females being more frequently strip searched when there are a smaller number of reasons--0-2 reasons--regarding their actions at the time of arrests. Specifically, this can translate to the fact that police more readily strip-search females compared to males even if the severity of their actions may not necessitate strip searching. Yet again, this hints at the potential of strip searching being sexually motivated and gendered, especially when there are mostly male police officers in Toronto [@policeStats] and where strip searching is notoriously regarded as a guise for sexual assault [@stripSearchNSW].

>>>>

---
title: "Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021"
title-block-banner: true
abstract: "Police strip search has always been a topic of great contention, where the question commonly raised was how certain demographics are more likely to undergo strip searches than others. Data then was gathered from Open Data Toronto to assess the correlation between strip searches and the racial and gender identities of arrested 'suspects' in the Toronto Municipal from 2020 to 2021. In short, this paper finds that police strip searches are slightly racialized and gendered, especially towards people of African descent and females within Toronto. This analysis would enable us to rethink the modern form of policing, how it transpires in times of crisis and critically affects people of marginalized identities." 
thanks: "Code and data are available at: https://github.com/ponolite/Police_Arrests_and_Strip_Searches/tree/main"
author: "Quang Mai"
date: today
date-format: long
format: pdf
editor: visual
toc: true
number-sections: true
bibliography: references.bib
output: 
  pdf_document:
    extra_dependencies: ["float"]
---

@@

Regarding @fig-reasons-gender, intriguingly, the graph calls into question of the above data confirming how males are slightly more likely to be strip searched compared to females when they're arrested. However, when intersected with data like the total number of reasons attributed to strip searches, there appears to be a different narrative. For strip searches that have 0 to 2 reason to be carried out, compared to the 10%, 28% and 29% of males, females prevail at 11%, 32% and 30% respectively. This equates to the fact that females are more frequently strip searched when there are a smaller number of reasons provided for their actions at the time of arrests. Specifically, this can translate to the fact that police more readily strip-search females compared to males even if the severity of their actions may not necessitate strip searching. Yet again, this hints at the potential of strip searching being sexually motivated and gendered, especially when there are mostly male police officers in Toronto [@policeStats] and where strip searching is notoriously regarded as a guise for sexual assault [@stripSearchNSW].
